conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-07-23 paper/paper.Rmd
Updated for JOSS format
Updated explanation on partial dependency plots, and how exponentiating them after adding them up together provides more 'realistic' numbers

# Abstract

@@

# Motivation / Introduction

@@

>>>>

# Summary

A summary describing the high-level functionality and purpose of the software for a diverse, non-specialist audience.

@@

# Statement of need

A Statement of need section that clearly illustrates the research purpose of the software and places it in the context of related work.

@@

Note that these partial dependency plots are on the log scale. 
When the six terms are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:

```{r}
# Show combined partial dep plot (i.e. sum of the partial dependencies for all six terms) in each setting: home, school, work and other
```

In other words, the six terms above provide patterns that are useful in modelling the different settings,
and correspond with real-life situations of how contact would look like. 
In the home setting for example, [ #TODO describe how children interact with parents and elderly generation, grandparents ].
When the terms for school and work are added, these terms also provide patterns that correspond with real-life situations.
https://idem-lab.github.io/conmat/dev/articles/visualising-conmat.html
In the school setting, children tend to contact other children in the same age groups as them.
In the work setting, there are no contacts with children under the age of ten and minimal contact with adults beyond retirement age.
